animbook: An R Package for Visualize \ldots{}

### 2023-09-04 animbook-journal.Rmd
introduction

---
title: "animbook: An R Package for Visualize ..."
date: Sys.Date()
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Faculty of Business and Economics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib

@@

@@

-------------------------------------------------------------------------------

# Data and Process

@@

-------------------------------------------------------------------------------

>>>>

---
title: "animbook: An R Package for Visualize ..."
date: 04/09/2023
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Faculty of Business and Economics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib

@@

With the increasing computational powers, animation with large amounts of data is now become more accessible than ever. With the inspiration from a New York Times article, "Extensive Data Shows Punishing Reach of Racism for Black Boys". The animation portrays the trajectory of how boys with different demographics could land up in society. With this plot in mind, the paper proposed a new visualization to help capture the movement of the observation for each different group over the specific period.

  This paper will focus on designing and validating the new visualization using a nested model (@nested_model) to offer an animation tool for conveying the observation trend in the given period. The cognitive theory of multimedia learning (@mayer_2005) will be considered during the designing period. This theory employs the structure and the strategies that will help the learner learn more effectively.

  The challenge of the New York Times article animation was the amount of code needed to reproduce. Additionally, the business data may or may not have the same information as the one in that article. It establishes a need to create tools for generalizing the animation to a wider range of data while still maintaining the main objective.

  The structure of this paper will consist of four main section. The first section is domain problem and data characterization, identifying the problems the visualization tools try to solve. Secondly, the operation and data type abstraction, the description of operations, and the types of data required for the next stage. The third section is visualization and interaction design, designing the visuals and refining the tools. In the last section, package design, develop the structure of the packages and how to implement the final visualize design into the R package. The checking of the threat and validating of that threat will be carried out throughout the entire process of designing the animbook package.

# Domain problem and data characterization

# Operation and data type abstraction

# Visualization and interaction design

# Package design

Introduction

@@

Data and Process

@@

### 2023-09-04 animbook-journal.tex
introduction

---
title: "animbook: An R Package for Visualize ..."
date: 04/09/2023
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Faculty of Business and Economics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Introduction

With the increasing computational powers, animation with large amounts of data is now become more accessible than ever. With the inspiration from a New York Times article, "Extensive Data Shows Punishing Reach of Racism for Black Boys". The animation portrays the trajectory of how boys with different demographics could land up in society. With this plot in mind, the paper proposed a new visualization to help capture the movement of the observation for each different group over the specific period.

  This paper will focus on designing and validating the new visualization using a nested model (@nested_model) to offer an animation tool for conveying the observation trend in the given period. The cognitive theory of multimedia learning (@mayer_2005) will be considered during the designing period. This theory employs the structure and the strategies that will help the learner learn more effectively.

@@

# Domain problem and data characterization

# Operation and data type abstraction

@@

# Visualization and interaction design

# Package design

@@

- The animated plot has not been used often in the business data presentation
- We want to see the movement of our variable of interest
- Business data: Accounting data (sales), Marketing data (customer interest), data analysis languages data
- Help with storytelling
- Inspiration: The New York Times (Extensive data shows punishing reach of racism for black boys). The animation plot shows what demographic group between white and black boys where would end up in society. It could be adapted to show, based on the demographic of the company, sees the movement of where they would end up. In the marketing data, the demographic of the customers could tell us the story of what product they preferred.

@@

- The data will need a following structure for it to be ready to plot: time index(time variable for the gganimate), x-axis for ggplot(this does not need to be the same as time index), key(unique identifier), rank(y-axis, factor variable), group(optional).

- The user can input any numerical, categorical and factor variable into the prep_anim function which will return the data in the format that the anim_plot function accepted. The x-axis and time index does not need to be the same as this allows for the user to reproduce the nytimes plot which is not time dependent. For the rank variable, no matter what the type of variable is in, it will return numerical variable.

@@

- The data structure
- The steps for the user
- How does the function processes the data

>>>>

% !TeX root = RJwrapper.tex
\title{animbook: An R Package for Visualize \ldots{}}
\author{by Krisanat Anukarnsakulchularp}

\maketitle

\abstract{%
An abstract of less than 150 words.
}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

With the increasing computational powers, animation with large amounts of data is now become more accessible than ever. With the inspiration from a New York Times article, ``Extensive Data Shows Punishing Reach of Racism for Black Boys''. The animation portrays the trajectory of how boys with different demographics could land up in society. With this plot in mind, the paper proposed a new visualization to help capture the movement of the observation for each different group over the specific period.

This paper will focus on designing and validating the new visualization using a nested model (Munzner (2009)) to offer an animation tool for conveying the observation trend in the given period. The cognitive theory of multimedia learning (Mayer (2005)) will be considered during the designing period. This theory employs the structure and the strategies that will help the learner learn more effectively.

@@

\hypertarget{domain-problem-and-data-characterization}{%
\section{Domain problem and data characterization}\label{domain-problem-and-data-characterization}}

\hypertarget{operation-and-data-type-abstraction}{%
\section{Operation and data type abstraction}\label{operation-and-data-type-abstraction}}

@@

\hypertarget{visualization-and-interaction-design}{%
\section{Visualization and interaction design}\label{visualization-and-interaction-design}}

\hypertarget{package-design}{%
\section{Package design}\label{package-design}}

@@

\begin{itemize}
\tightlist
\item
  The animated plot has not been used often in the business data presentation
\item
  We want to see the movement of our variable of interest
\item
  Business data: Accounting data (sales), Marketing data (customer interest), data analysis languages data
\item
  Help with storytelling
\item
  Inspiration: The New York Times (Extensive data shows punishing reach of racism for black boys). The animation plot shows what demographic group between white and black boys where would end up in society. It could be adapted to show, based on the demographic of the company, sees the movement of where they would end up. In the marketing data, the demographic of the customers could tell us the story of what product they preferred.
\end{itemize}

@@

\begin{itemize}
\item
  The data will need a following structure for it to be ready to plot: time index(time variable for the gganimate), x-axis for ggplot(this does not need to be the same as time index), key(unique identifier), rank(y-axis, factor variable), group(optional).
\item
  The user can input any numerical, categorical and factor variable into the prep\_anim function which will return the data in the format that the anim\_plot function accepted. The x-axis and time index does not need to be the same as this allows for the user to reproduce the nytimes plot which is not time dependent. For the rank variable, no matter what the type of variable is in, it will return numerical variable.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The data structure
\item
  The steps for the user
\item
  How does the function processes the data
\end{itemize}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-mayer_2005}{}}%
Mayer, Richard E. 2005. {``Cognitive Theory of Multimedia Learning.''} In \emph{The Cambridge Handbook of Multimedia Learning}, edited by RichardEditor Mayer, 31--48. Cambridge Handbooks in Psychology. Cambridge University Press. \url{https://doi.org/10.1017/CBO9780511816819.004}.

\leavevmode\vadjust pre{\hypertarget{ref-nested_model}{}}%
Munzner, Tamara. 2009. {``A Nested Model for Visualization Design and Validation.''} \emph{IEEE Transactions on Visualization and Computer Graphics} 15 (6): 921--28. \url{https://doi.org/10.1109/TVCG.2009.111}.

\end{CSLReferences}

\bibliography{RJreferences.bib}

\address{%
Krisanat Anukarnsakulchularp\\
Monash University\\%
Faculty of Business and Economics\\ Melbourne, Australia\\
%
%
\textit{ORCiD: \href{https://orcid.org/0009-0008-5638-7124}{0009-0008-5638-7124}}\\%
\href{mailto:kanu0003@student.monash.edu}{\nolinkurl{kanu0003@student.monash.edu}}%
}
